Download data

### 2024-02-28 scripts/subsetDataforCrews.Rmd
fn to write out summaries

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(X = teams_list[1], 
       FUN = phen_tabulator,
       path = p2ts, 
       admu = admin_boundaries, 
       target_species = spp_needed
       )

focal_area <- dplyr::filter(admin_boundaries, ADMU_NA == str_to_upper('St. George Field Office' )) |>
  sf::st_union() |>
  sf::st_transform(5070) |>
  vect()

focal_r <- rast(file.path(path, f[[1]]))
out_v <- terra::extract(focal_r, focal_area, method = 'simple', fun = table, na.rm = T, ID = FALSE)
pos <- unlist(lapply(out_v, function(x){x1 <- colnames(x)[which.max(x)]})) # most common doy for event

>>>>

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
oppy <- lapply(X = teams_list[1], 
       FUN = phen_tabulator,
       path = p2ts, 
       admu = admin_boundaries, 
       target_species = spp_needed
       )

tdf <- oppy[[1]] |>
  dplyr::arrange(taxon)

tdf <- dplyr::left_join(tdf, dates[[1]], by = 'doy')

dates <- date_maker()
